---
title: "Tidy Data in Education"
author: "Joshua de la Bruere"
date: "10/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is Tidy Data

When it comes to data analysis the idea of "Tidy Data" comes up fairly often. It has a few other names like model matrix, or the Boyce-Codd 3rd normal form. Getting data into a Tidy format is often the first step in preforming analysis in an efficent manner. 

The main principles of "Tidy Data" are that each row is an observation and each column is a variable. 

Consider this example of data for analysiing if a student is at-risk. 
```{r}
tibble::tribble(
~student_id, ~last_name, ~first_name, ~grade, ~absences,  ~missing_assignments,
"170100", "Kirk", "James", "09", 6, 10,
"163405", "Skywalker", "Luke","12", 2, 0,
"122300", "Watson", "John", "10", 0, 1 ,
"103064", "Frye", "Kaylee","11", 5, 3,
"110110", "Pond", "Amy", "12", 9, 2

) %>% gt()
```
Each column represents a variable that is consistant throughout. Student ID is always the student's ID, the names are alaways the names, and absences is only ever absences. 

